Report on Lab 1 \& Lab 2 in EDA282, Parallel Computer Organization and Design

### 2014-10-14 lab/report/include/lab1.tex
wrote

\subsection{Task 3}
\label{sec:lab13}
\todo[inline]{
Compare MESI and MESI+migratory.
Why is one better than the other?
How does the behavior change when the dataset size changes?}

>>>>

\subsection{Task 3}
\label{sec:lab13}
\todo[inline]{
Compare MESI and MESI+migratory.
Why is one better than the other?
How does the behavior change when the dataset size changes?}
MESI-MG is a modified version of MESI where the S state is not utilized. If a cache reads a data element it will be forwarded from a remote private cache if it holds the data element in the E or M state, and then the remote cache invalidates it's copy.
